Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-06-29 write-up/covid-writeup.tex
Editing the first analysis of sample / checking'

We start with using Table~\ref{tab:indiana} to compute IPW weights.  The random sample is $n=3,658$.  Here, we demonstrate how to compute the weight for a particular strata.  For example, the strata defined as Male, 40--59, White, has a Fever, no household cases, and no prior tests has a weight proportional to
$$
\frac{\left( 0.493 \times 0.252 \times 0.869 \times 0.018 \right)}{\left(0.418 \times 0.411 \times 0.231 \times 0.17 \right)} = 0.628
$$
Using the constructed weights and the adjusted strata-level prevalence estimates, the IPW estimate under no measurement-error is $7.7$, a decrease of four percentage points from the observed prevalence of $11.7$. Using Table~\ref{tab:indiana} to compute weights requires the assumption of independence among factors.  To alleviate this, we compute weights using Facebook's survey data collected in Indiana over that window of time; the resulting IPW estimate under no measurement-error is

>>>>

% FP: https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7307014/
% FN: https://www.medrxiv.org/content/10.1101/2020.04.16.20066787v2.full.pdf

We start by using Table~\ref{tab:indiana} to compute IPW weights for end of April, early May.  The random sample is $n=3,658$ and IPW weights are computed per strata which depend on Gender, Age, Race, Fever, Positive Case in Household, and Prior Positive Test.  The weight for the strata defined as Male, 40--59, White, has a Fever, no household cases, and no prior tests is proportional to:
$$
\frac{\left( 0.493 \times 0.252 \times 0.869 \times 0.018 \right)}{\left(0.418 \times 0.411 \times 0.231 \times 0.17 \right)} = 0.628
$$
Using the constructed weights and the adjusted strata-level prevalence estimates, the IPW estimate under no measurement-error is $7.7$, a decrease of four percentage points from the observed prevalence of $11.7$. Using Table~\ref{tab:indiana} to compute weights requires the assumption of independence among factors.  To alleviate this, we compute weights using Facebook's survey data collected in Indiana over that window of time; the resulting IPW estimate under no measurement-error is
